Finding the True MVP

### 2024-12-03 paper/paper.qmd
Render terst finally worked !!

\$\$

MVP\_{Index} = 0.8PTS\_{Norm} + 0.25AST\_{Norm} + 0.25TRB\_{Norm} + 0.1STL\_{Norm} + 0.1BLK\_{Norm} + 0.15WS\_{Norm}

\$\$

@@

-   `Player:` The name of the NBA player.
-   `Year:` The year in which the player was selected as MVP.
-   `Tm:` The three letter designation for the NBA team the player played for the year.
-   `G:` Games played by the player.
-   `MP:` Minutes played per game.
-   `PTS:` Points per game.
-   `TRB:` Total Rebounds per game, including offensive and defensive rebounds.
-   `BLK:` Blocks per game
-   `STL:` Steals Per game
-   `WS:` The amount of wins allocated to the individual player

@@

merged_real_mvp <- merged_real_mvp %>%
  mutate(
    Year = case_when(
      # If entry matches "YYYY-YY", extract the first 4 characters as the year
      grepl("^\\d{4}-\\d{2}$", Season) ~ as.numeric(substr(Season, 1, 4)) + 1,

      # If entry matches "Mmm-YY", extract the last 2 characters, convert to 20YY, and add 1
      grepl("^[a-zA-Z]{3}-\\d{2}$", Season) ~ as.numeric(paste0("20", substr(Season, 5, 6))) + 1,

      # Default: NA for non-matching formats
      TRUE ~ NA_real_
    )
  )

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \pi_i + \alpha_i + \rho_i + \beta_i + \xi_i + \omega_i \\
\mu &\sim \mbox{Normal}(0, 2.5) \\
\pi &\sim \mbox{Normal}(0, 2.5) \\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\rho &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\xi &\sim \mbox{Normal}(0, 2.5) \\
\omega &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```

```{r}
# create a linear regression model
lm_model <- lm(MVP_index ~ PTS + AST + TRB + BLK + STL + WS, data = nba_master)

@@

# Create a styled table using kable
combined_table %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    col.names = c(
      "Year",
      "Simulated Data - Player",
      "Simulated Data - MVP Index",
      "Historical Data - Player",
      "Historical Data - MVP Index"
    )
  ) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  add_header_above(c(" " = 1, "Simulated Data" = 2, "Historical Data" = 2))

>>>>

$$

MVP_{Index} = 0.8PTS_{Norm} + 0.25AST_{Norm} + 0.25TRB_{Norm} + 0.1STL_{Norm} + 0.1BLK_{Norm} + 0.15WS_{Norm}

$$

@@

-`Player:` The name of the NBA player.
-`Year:` The year in which the player was selected as MVP.
-`Tm:` The three letter designation for the NBA team the player played for the year.
-`G:` Games played by the player.
-`MP:` Minutes played per game.
-`PTS:` Points per game.
-`TRB:` Total Rebounds per game, including offensive and defensive rebounds.
-`BLK:` Blocks per game
-`STL:` Steals Per game
-`WS:` The amount of wins allocated to the individual player

@@

merged_real_mvp <- merged_real_mvp %>%
  mutate(
    Year = case_when(
      grepl("^\\d{4}-\\d{2}$", Season) ~ as.numeric(substr(Season, 1, 4)) + 1,
      grepl("^[a-zA-Z]{3}-\\d{2}$", Season) ~ as.numeric(paste0("20", substr(Season, 5, 6))) + 1,
      TRUE ~ NA_real_
    )
  )

@@

\begin{align}
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \pi_i + \alpha_i + \rho_i + \beta_i + \xi_i + \omega_i \\
\mu &\sim \mbox{Normal}(0, 2.5) \\
\pi &\sim \mbox{Normal}(0, 2.5) \\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\rho &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\xi &\sim \mbox{Normal}(0, 2.5) \\
\omega &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

```{r}

# create a linear regression model
lm_model <- lm(MVP_index ~ PTS + AST + TRB + BLK + STL + WS, data = nba_master)

@@

print(combined_table)
